---
title: "start_2_R_basics"
output:
  pdf_document: default
  html_notebook: default
---

```
In R, an object is anything that can be assigned to a variable. This includes constants,
data structures, functions, and even graphs. Objects have a mode (which describes
how the object is stored) and a class (which tells generic functions like print how
to handle it).
```
#

```
Vectors are one-dimensional arrays that can hold numeric data, character data, or logi-
cal data. The combine function c() is used to form the vector.
```

```{r}
x <- c(1,2,4) #The “c" stands for “concatenate."
x
q <- c(x,x,8)
q
#
a <- c(1, 2, 5, 3, 6, -2, 4)
b <- c("one", "two", "three")
c <- c(TRUE, TRUE, TRUE, FALSE, TRUE, FALSE)

```

#
```
Seen Above -- a is numeric vector, b is a character vector, and c is a logical vector. Note that the
data in a vector must only be one type or mode (numeric, character, or logical). You
can’t mix modes in the same vector.
```
#
```
Indexing vectors - 
#
a_idx_1_3 <- a[c(1:3)]
```
#
```{r}
a_idx_1_3 <- a[c(1:3)]
a_idx_1_3
print(a_idx_1_3)

# x <- c(1,3,4) #The “c" stands for “concatenate."
# x
# q <- c(x,x,8)
# q
```

```{r}
x <- c(1,3,4) #The “c" stands for “concatenate."
x
q <- c(x,x,8)
q
```


```{r}
x <- c(1,7,4) #The “c" stands for “concatenate."
x
q <- c(x,x,8)
q
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it 
(click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. 
Consequently, unlike *Knit*, *Preview* does not run any R code chunks. 
Instead, the output of the chunk when it was last run in the editor is displayed.
