---
title: "start_2_R_basics"
output:
  pdf_document: default
  html_notebook: default
---

```
In R, an object is anything that can be assigned to a variable. This includes constants,
data structures, functions, and even graphs. Objects have a mode (which describes
how the object is stored) and a class (which tells generic functions like print how
to handle it).
```
#

```
Vectors are one-dimensional arrays that can hold numeric data, character data, or logi-
cal data. The combine function c() is used to form the vector.
```

```{r}
x <- c(1,2,4) #The “c" stands for “concatenate."
x
q <- c(x,x,8)
q
#
a <- c(1, 2, 5, 3, 6, -2, 4)
b <- c("one", "two", "three")
c <- c(TRUE, TRUE, TRUE, FALSE, TRUE, FALSE)

```

#
```
Seen Above -- a is numeric vector, b is a character vector, and c is a logical vector. Note that the
data in a vector must only be one type or mode (numeric, character, or logical). You
can’t mix modes in the same vector.
```
#
```
Indexing vectors - 
#
a_idx_1_3 <- a[c(1:3)]
```
#
```{r}
a_idx_1_3 <- a[c(1:3)]
a_idx_1_3
print(a_idx_1_3)

# x <- c(1,3,4) #The “c" stands for “concatenate."
# x
# q <- c(x,x,8)
# q
```
#
```
A matrix is a two-dimensional array where each element has the same mode (numeric,
character, or logical). Matrices are created with the matrix function
#
The option byrow indicates whether the matrix should be filled in
by row ( byrow=TRUE ) or by column ( byrow=FALSE ). The default is by column.
```
#
```
myymatrix <- matrix(vector, nrow=number_of_rows, ncol=number_of_columns,
byrow=logical_value, dimnames=list(
char_vector_rownames, char_vector_colnames))
```



```{r}
matrx_y <- matrix(1:20, nrow=5, ncol=4)
matrx_y
```

#### Read CSV 
#

```{r}
library(readr)
df_iris <- read_csv("~/temp/11_22/#Rstats/RStudio_Nov22/git_up/rstats_nov22/iris.csv")
df_iris_1 <- read_csv("~/temp/11_22/#Rstats/RStudio_Nov22/git_up/rstats_nov22/iris_1.csv") ## Dummy IRIS - for testing some simple code 
View(df_iris)
```

<!-- ── Column specification ────────────────────────────────────────────────────────────────────────────────────────────────────
Delimiter: ","
chr (1): Species
dbl (4): Sepal.Length, Sepal.Width, Petal.Length, Petal.Width

ℹ Use `spec()` to retrieve the full column specification for this data.
ℹ Specify the column types or set `show_col_types = FALSE` to quiet this message. -->

#### Get DF Cols 
#

```{r}
print(df_iris$Species)
vector_species <- df_iris$Species
print(class(vector_species))
```

#### Check Duplicates 
#

```{r}
print(class(vector_species))
duplicated(vector_species)
print(length(vector_species))#150 

sum(duplicated(vector_species)) 
# 147 - as the 1st Occurences are Not considered as DUPLICATES

# print(nrow(vector_species))#NULL -- Its a VECTOR NOT a DF 
# print(ncol(vector_species)) # NULL-- Its a VECTOR NOT a DF  
```


#### Merge 2 Data Sets 
#

```{r}
# df_merged_iris <- merge(df_iris,df_iris_1,by="Species",all.x=TRUE,all.y=TRUE)
# #View(df_merged_iris)
# print(nrow(df_merged_iris))## nrow 
# print(ncol(df_merged_iris)) ## ncol

```

#### Order Data in a DATA FRAME 
#

```{r}
#order_iris <- df_iris[order[df_iris$Species]]
#Error in order[df_iris$Species] : 
#object of type 'closure' is not subsettable

order_iris <- df_iris[order(df_iris$Species),]
order_iris_1 <- df_iris[order(df_iris$Species , df_iris$Sepal.Length),] 
#Sepal.Length, 
order_iris_2_ascending <- df_iris[order(df_iris$Species , df_iris$Sepal.Width),]
order_iris_2_decending <- df_iris[order(df_iris$Species , - df_iris$Sepal.Width),]
#Sepal.Width, 
#
print(class(order_iris)) #[1] "spec_tbl_df" "tbl_df"      "tbl"         "data.frame" 
print(head(order_iris))
print(tail(order_iris))

#
print(head(order_iris_1)) ###Sepal.Length, 
print(tail(order_iris_1)) ###Sepal.Length, 

#
print(head(order_iris_2_decending)) ##Sepal.Width, 
print(tail(order_iris_2_decending)) ##Sepal.Width, 

# TODO - Petal.Length, Petal.Width
# print(nrow(df_merged_iris))## nrow 
# print(ncol(df_merged_iris)) ## ncol

```

#

##### AS TIBBLE 

- https://github.com/tidyverse/tibble/blob/HEAD/R/as_tibble.R
- https://tibble.tidyverse.org/reference/as_tibble.html

#

# remotes::install_github("thinkr-open/golem")

```{r}
library(dplyr)
tibble_order_iris_2_decending <- as_tibble(order_iris_2_decending)
print(head(tibble_order_iris_2_decending))
```


```{r}
library(dplyr)
tibble_order_iris_2_decending <- as_tibble(order_iris_2_decending)
print(head(tibble_order_iris_2_decending))
```


```{r}

tibble_order_iris_2_ascending <- as_tibble(order_iris_2_ascending)
print(head(tibble_order_iris_2_ascending))
```


##### Horizontal Join -- two data frames are joined by one or more common key variables (that is
an inner join).
#


```{r}

```





```{r}

```






```{r}

```






```{r}

```





```{r}

```



#### Import CSV from WWW
#

```{r}
# #https://www.rdocumentation.org/packages/utils/versions/3.6.2/topics/read.table
# www <- "http://www.massey.ac.nz;-pscowper/ts/cbe.dat"
# CBE <- read.table(www, header = T)
```






```{r}

```




```{r}

```


```{r}

```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it 
(click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. 
Consequently, unlike *Knit*, *Preview* does not run any R code chunks. 
Instead, the output of the chunk when it was last run in the editor is displayed.
